### 2024-03-06 Scripts/Manuscript/manuscript.Rmd
added (suggested) changes to methods section, and made the first appendix containing additional models and results.

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking as measures, which did not match this study's focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the final unit of measurement. Here primary measures refers to measures assessing variables included in the primary test of the replication, were used. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.. The result was a total sample size of 77 measures. The Table BELOW show descriptive information about the data for each Many Labs Project.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information were used as the datasets in the analysis.

@@

FOOTNOTE:The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

@@

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies. Descriptions of the extracted variables can be found in the [Measures](#Measures) section below. Exact descriptions of the search strategy can be found in Appendix ???.

@@

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.

@@

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach]. Hpowever, in the supplementary materials ???, Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

@@

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs coded across both original articles and replication protocols. QMPs were all coded to be either true, false, or not applicable. Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified. Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement. An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable)

@@

```{=tex}
\begin{equation}
QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin and justifications can be seen in Appendix ???.

APPENDIX: on item revision and origin

@@

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

@@

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 36, 54, 57, 60, 63)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)

@@

@@

@@

Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```
All of these models assume that the QMPs are the same across each replication set. This was necessary as only one protocol was available for coding per replication set. The assumption was deemed likely to hold, since each replication within a set was based on the same protocol containing all the measurement details that were reported and upon which measurement was based.

@@

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study. For hypothesis 5 a similar formula was used [[[change to logistic regression, with footnote that pre-reg was inverted]]]:

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
\end{equation}
```
Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main). Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

```{r Hypothesis5Model, include = FALSE}
## Hypothesis 5 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

H5_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)

@@

The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6. The outcome variable remains the same as in the model for hypothesis 5. The independent variable is changed to the QMP ratio for original articles. The resulting model formula is as follows:

@@

These models had independence of observations as an assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects. In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses. As of writing this article the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.

@@

```{r Hypothesis6Associations, include = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
# of a concern for the revised.

# Associations between the QMP categories (revised QMP coding)
Results_H6_between_REV <- Associations_H6_REV(data_h6)

### Exploratory Analyses {#ExploratoryAnalyses}

Follow-up analyses were preregistered for hypothesis 6. Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Due to the large number of tests, the focus was exploratory using visualisation rather than inference.

APPENDIX:

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.2_clean, data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

# creating an empty dataframe to store the results in
cfa_results <- data.frame(RMSEA = 0,
                          N_factors = 0,
                          Single_factor = "")

# running the cfas for all of the extracted datasets
for (i in 1:length(extracted_data_list)){
  # obtaining single factor model cfa RMSEA value for evaluation
  RMSEA_value <- fa(extracted_data_list[[i]][-1])$RMSEA[1]

  if(is.null(RMSEA_value) != TRUE){
    RMSEA_value <- apa_num(RMSEA_value, digits = 3)
  }

  # conducting parallel test to check if one factor solution is best.
  parallel_N_factors <- fa.parallel(extracted_data_list[[i]][-1], 
                                    fa = "fa")$nfact

  # adding a single factor check indicator value
  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, "Yes", 
                          "No")

  # adding the cfa results of one factor analysis to the results dataframe.
  cfa_results <- rbind(cfa_results, c(RMSEA_value, parallel_N_factors, 
                                      single_factor))
}

# removing the initial empty row
cfa_results <- cfa_results[-1,]

@@

Based on a chi square comparison, reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`). These results are contradictory to hypothesis 1.

The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. These results are in line with hypothesis 2. However, the measures with lower average reliabilities did show a large amount of variation in the reliability coefficient as can be seen figure \@ref(fig:Plot23AlphaCode)

The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable. The results of the logistic and multilevel sensitivity analysis models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for Cronbach's alpha.

[???sensitivity analyses??? to appendix]

```{r ReplicabilityReliabilityTestTable, warning = FALSE}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_test_result_main_alpha$full_result$alpha`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)). This is contradictory to the expectation in hypothesis 3. Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see supplementary materials ???). However, caution should be taken in evaluating the results from these analyses should, given the small sample number of measures used to estimate the models for these tests.

[other relevant info such as: ???]

@@

Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols. Results showed that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects (`r betareg_output_to_apa_full(H4_test_results_REV)`). This result is in line with hypothesis 4.

A similar beta-regression tested the association between replication success and QMP ratio in replication protocols. Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`).

```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.01, height = 0.01) +
  stat_smooth(method="lm") + 
  theme_minimal() +
  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  ylab("QMP Replication Ratio") +
  xlab("QMP Ratio")

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6. Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually. However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).

@@

[[[APPENDIX??? sensitivity analyses and so on: Planned exploratory analyses were preformed to expand on the test for hypothesis 6. The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately. Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of the revised QMP ratios from different QMP types between replication protocols and original articles. As shown in the figure, no relation was strong and highly stable, and even fewer were consistent between initial and revised coding protocols. ]]] IF SO, check rest of article to remove this part by in large.

[[[OMIT: The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs. All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.]]]

@@

```{r Plot46FullRevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line. The abbreviations on the axes relate to the QMP categories described in Table 1: Def. is definition, Op. is operationalization, Sel. is selection/creation, Quant. is quantification, and Mod. is modification. The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols. Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

[[[TO APPENDIX sensitivity analyses: Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol. INCLUDING TABLES]]]

```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
  Results_H6_between_REV$tot_mod)

>>>>

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was created in Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study's focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.. The result was a total sample size of 77 measures. The Table BELOW show descriptive information about the data for each Many Labs Project.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio]. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information were used as the datasets for their respective analyses.

@@

FOOTNOTE: The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

@@

@@

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.

@@

Relevant primary measures were identified by combing through the entirety of the methods section for each preregistered replication protocol. Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies. Descriptions of the extracted variables can be found in the sections below. The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the supplementary materials ???.

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses as it is one of the most popular [@cho2015cronbach]. Analyses based on the Omega can be found in Appendix ???. Omega was included since it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

@@

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs coded across both original articles and replication protocols. QMPs were all coded to be either true, false, or not applicable. Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified. Each coded QMP belonged to one of five QMP type categories that were derived from the classification in @flake2020measurement. An overview of the QMP categories of the coding variables can be seen in Table \@ref(tab:QMPCodingInfoTable).

@@

```{=tex}
\begin{equation}
QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin and justifications can be seen in Supplementary Materials ???.

FOOTNOTE: additional analyses, tables and figures based on QMPs obtained with the initial protocol can be found in Appendix ???.

???Supplementary Materials: on item revision and origin

@@

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.???

@@

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)

@@

# adding OR to the result
H3_main_full_results_alpha_with_OR <- OR_to_apa_full_supplier(H3_test_result_main_alpha$full_result$alpha, negative_b = FALSE)

# well this OR is quite a ridiculous number now..., but then again a step from 0 alpha to 1, is quite a jump too...

@@

???Put in appendix???:

@@

Hypothesis 4 & 6 were both tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```

These models assume that the QMPs are the same across each replication set. This was necessary as only one protocol was available for coding per replication set. The assumption was deemed likely to hold, since each replication within a set was based on the same protocol containing all the measurement details that were reported and upon which measurement was based.

@@

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study. For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^2].

[^2]: This analysis differs from what was pre-registered. Initially this analysis was also a beta-regression where QMP ratio was the outcome variable, while replication success was the predictor. The pre-registered analysis outcomes are available in Appendix ???A???.

```{=tex}
\begin{equation}
logit(replicated_{i}) = \beta_{0} + \beta_{1} QMP\_ratio_{i} (\#eq:H5Main)
\end{equation}
```

Where $replicated$ is a dummy coded variable, which is the same as for equation \@ref(eq:H3Main), and $logit(.)$ refers to the logit link function commonly used for logistic regression models. Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

```{r Hypothesis5Model, include = FALSE}
## Hypothesis 5 logistic regression model
H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))

H5_test_results_REV <- apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))

H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)

H5_test_results_REV_with_OR <- OR_to_apa_full_supplier(H5_test_results_REV$full_result$QMP_REV_ratio, negative_b = TRUE)

@@

The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6. The outcome variable is the same as the predictor in the model for hypothesis 5. The independent variable in this model is instead the QMP ratio for the original articles. The resulting model formula is as follows:

@@

APPENDIX:"These models had independence of observations as an assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects. In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models with each Many Labs project as a group were implemented as sensitivity analyses. As of writing this article the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model. ???FOOTNOTE: exploratory analyses were preregistered for this but left out.???

@@

@@

Figure ... already demonstrates that multiple item measures are most commonly not accompanied by a reported reliability coefficient in neither original articles nor replication protocols. Additionally, when comparing between the two using a chi square comparison, it was observed that in replication protocols reliability coefficients are reported significantly less often than in original articles ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`). These results are contradictory to hypothesis 1.

The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`. Because this number is larger than .5, it suggests that variance was larger between replication sets than within. A more sophisticated, albeit not pre-registered, test based on the Tau heterogeneity estimate and Q-test for heterogeneity obtained from a meta-analysis of the calculated reliability coefficients was additionally performed to test hypothesis 2. Figure \@ref(fig:Plot23AlphaCode) shows that there is quite some variance in Tau (the indicator of true differences in reliability scores between labs) with some having a Tau estimate of approximately 0, and others reaching beyond .1, which suggests that ???the true variance in reliability for that measure is as large as .1 point of Cronbach's alpha???. Based on the Q-test for heterogeneity, ???5??? out of the total of ???18??? estimates of heterogeneity were judged to be significant. However, the Q-test and tau are both highly sensitive to the number of studies in the meta-analyses (CITATION HERE), which may explain some of the results.

Therefore, while evidence for heterogeneity would not be in line with hypothesis 2, the evidence remains inconsistent when looking across all studies, and sensitive to the sample size of the meta-analyses.

In figure ... the calculated reliabilities were separated by a red line based on whether the replications the measures mere used in were successful when judged at a meta-analytic significance level of .05. A logistic regression was performed to detect if there was indeed a relation between calculated reliabilities and replication success.

Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`), nor in any of the multilevel sensitivity analyses models (see Appendix ???). This is contradictory to the expectation in hypothesis 3. Similar results were found for the analyses when using Omega as the reliability coefficient of choice (see Appendix ???). However, caution should be taken in evaluating these results, given the small sample number of measures used to estimate the models and the resulting large uncertainty around the estimate.

@@

The bottom pannel of Figure \@ref(fig:Plot456Code) already shows that original articles contained a significantly larger proportion of QMPs than replication protocols for the measures of the same effects. Beta-regression was used to test the difference in QMP ratio between original articles and replication protocols. The results of this test indicated that this difference was significant (`r betareg_output_to_apa_full(H4_test_results_REV)`). This result is in line with hypothesis 4.

A similar beta-regression tested the association between replication success and QMP ratio in replication protocols. Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r H5_test_results_REV_with_OR`). However, this result did not hold for the QMP ratios obtained with the initial coding protocol (`r H5_test_results_with_OR`).

???Footnote: analysis was changed from the pre-registered beta-regression to logistic regression for interpretation sake, significance did not change between the two. The original beta-regression results can be found in Appendix ???

```{r Plot46RevisedDataCode, error = FALSE, warning = FALSE, fig.cap = "Scatterplot of original and replication total QMP ratio’s with linear regression line. Each dot in the figure describes the QMP ratio in that graph across both the original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
ggplot(plot_46_data_rev[plot_46_data_rev$QMP_type == "QMP.Ratio" & plot_46_data_rev$QMP_Rep_type == "Rep.QMP.Ratio",], aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.01, height = 0.01) +
  stat_smooth(method="lm") + 
  theme_minimal() +
  theme(strip.text.y = element_text(size = 7), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  ylab("QMP Ratio (Replication Protocol)") +
  xlab("QMP Ratio (Original Article)") 
```

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. It showed that total QMP ratio in the original article can significantly relates to the total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6. Figure \@ref(fig:Plot46RevisedDataCode) displays this relationship visually. However, similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`).

@@

@@

```{r ReplicabilityReliabilityTestTable, warning=FALSE}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

@@

[[[TO APPENDIX initial analyses: Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol. INCLUDING TABLES]]]
